\section{Evaluation}
\label{sec:evaluation}

We evaluate CCV along four research questions:

\begin{itemize}
    \item \textbf{RQ1}: How often do LLM agents hallucinate about code?
    \item \textbf{RQ2}: Does deterministic verification catch hallucinations that LLM-as-judge misses?
    \item \textbf{RQ3}: Does claim-calibrated confidence improve downstream decision quality?
    \item \textbf{RQ4}: Which claim types are most commonly hallucinated?
\end{itemize}

\subsection{Dataset}

We construct a controlled evaluation dataset from synthetic fixture repositories with known ground truth. Each sample consists of a reasoning text (simulating LLM agent output), a fixture repository, and manually annotated claims with expected verdicts.

\textbf{Fixture repositories.} Three repositories spanning Python, Go, and TypeScript, containing known functions, imports, lockfiles, and deliberate patterns for each claim type. The Python fixture includes aliased imports (\texttt{import subprocess as sp}), indirect function references (\texttt{tl = torch.load}), and class-based call patterns to test verifier limitations.

\textbf{Dataset composition.} 40 reasoning samples yielding 50 annotated claims across 11 of 14 claim types. Claims are split into: 31 expected-\textsc{Verified} (correct assertions), 19 expected-\textsc{Refuted} (hallucinated assertions), covering both straightforward cases and adversarial edge cases (aliased calls, out-of-range line numbers, wrong package versions).

\textbf{Limitations of controlled evaluation.} This dataset validates verifier correctness against known ground truth. A full-scale evaluation on real agent reasoning (500+ claims from production triage) is planned as follow-up work. The controlled setting is sufficient to measure per-type accuracy and calibration but cannot measure extraction recall on real LLM outputs.

\subsection{Baselines}

\begin{itemize}
    \item \textbf{No verification}: Agent confidence as-is (current practice).
    \item \textbf{CCV}: Typed extraction + deterministic verification (our system).
    \item \textbf{Ablation A}: Typed extraction + LLM-judge verification. Isolates the value of deterministic verification over LLM-as-judge. \emph{(Planned for full-scale evaluation.)}
    \item \textbf{Ablation B}: Claimify-style extraction + deterministic verification. Isolates the value of our typed taxonomy over generic claim extraction. \emph{(Planned for full-scale evaluation.)}
    \item \textbf{Human expert}: Manual verification by a developer familiar with the codebase (upper bound).
\end{itemize}

\subsection{Metrics}

\textbf{Extraction quality.} Precision and recall of extracted claims against ground truth, with matching defined as: same claim type and all ground-truth parameter keys present with equal values.

\textbf{Verification accuracy.} Proportion of correct verdicts, broken down by claim type. We report false-\textsc{Refuted} rate (most dangerous: could override correct conclusions) and false-\textsc{Verified} rate separately.

\textbf{Calibration.} Per-type accuracy table comparing hardcoded method confidence values against empirical correctness rates. Expected Calibration Error (ECE)~\cite{naeini2015calibration} as aggregate metric.

\textbf{Downstream impact.} For RQ3, we measure the change in triage accuracy when CCV's action (\textsc{Boost}/\textsc{Flag}/\textsc{Override}) is applied to the agent's original verdict.

\subsection{Results}

\subsubsection{RQ1: Hallucination Frequency}

Of 50 claims in our dataset, 19 (38\%) represent hallucinated assertions (expected verdict: \textsc{Refuted}). CCV correctly identified 18 of 19 hallucinations (Table~\ref{tab:rq1}). Two claims returned \textsc{Unverifiable} rather than the expected verdict: one due to a lockfile format mismatch (Go module path not in go.sum), and one due to a missing advisory database for CVE version checking.

\begin{table}[t]
\centering
\caption{Claim verification results across 50 annotated claims from 3 fixture repositories.}
\label{tab:rq1}
\small
\begin{tabular}{lrrr}
\toprule
& \textbf{Verified} & \textbf{Refuted} & \textbf{Unverifiable} \\
\midrule
Count & 30 & 18 & 2 \\
Percentage & 60\% & 36\% & 4\% \\
\bottomrule
\end{tabular}
\end{table}

The 4\% \textsc{Unverifiable} rate reflects CCV's design choice: when the verification method cannot produce a reliable answer (missing lockfile, unsupported advisory database), it returns \textsc{Unverifiable} rather than guessing. This satisfies the safety desideratum (Section~\ref{sec:problem}).

\subsubsection{RQ2: Deterministic vs. LLM-Judge Verification}

On the controlled dataset, CCV achieves 96\% verification accuracy with zero false-\textsc{Refuted} and zero false-\textsc{Verified} errors (Table~\ref{tab:rq2}). The 4\% gap is entirely \textsc{Unverifiable} results, not incorrect verdicts.

\begin{table}[t]
\centering
\caption{Verification accuracy on controlled dataset ($n=50$). Ablation baselines require full-scale evaluation.}
\label{tab:rq2}
\small
\begin{tabular}{lrrr}
\toprule
\textbf{Method} & \textbf{Accuracy} & \textbf{False Ref.} & \textbf{False Ver.} \\
\midrule
CCV (deterministic) & 0.96 & 0.00 & 0.00 \\
Ablation A (LLM-judge) & \multicolumn{3}{c}{\emph{planned}} \\
Human expert & \multicolumn{3}{c}{\emph{planned}} \\
\bottomrule
\end{tabular}
\end{table}

The zero false-\textsc{Refuted} rate is notable: this is the most dangerous error mode, as it could cause CCV to override a correct triage verdict. Deterministic verification provides this guarantee by construction for the claim types it covers.

\subsubsection{RQ3: Downstream Impact}

Table~\ref{tab:rq3} shows CCV's action distribution across the 40 reasoning samples. Samples with all claims verified receive \textsc{Boost} (increased confidence). Samples containing hallucinated claims receive \textsc{Flag} or \textsc{Override}, correctly identifying unreliable reasoning.

\begin{table}[t]
\centering
\caption{CCV action distribution across 40 reasoning samples.}
\label{tab:rq3}
\small
\begin{tabular}{lrr}
\toprule
\textbf{Action} & \textbf{Count} & \textbf{Percentage} \\
\midrule
\textsc{Boost} (all claims verified) & 22 & 55\% \\
\textsc{Flag} (50--79\% verified) & 6 & 15\% \\
\textsc{Override} ($<$50\% verified) & 8 & 20\% \\
\textsc{No\_Change} (no claims) & 4 & 10\% \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{RQ4: Per-Type Hallucination Analysis}

Table~\ref{tab:rq4} breaks down verification accuracy and calibration by claim type. All claim types achieve 100\% accuracy except \textsc{Package\_Version} (75\%), where two claims involving Go module paths returned \textsc{Unverifiable} due to lockfile format handling.

\begin{table}[t]
\centering
\caption{Per-type verification accuracy and calibration ($n=50$). ``Conf.'' is the hardcoded method confidence; ``Actual'' is observed accuracy on this dataset.}
\label{tab:rq4}
\small
\begin{tabular}{lrrrr}
\toprule
\textbf{Type} & \textbf{$n$} & \textbf{Acc.} & \textbf{Conf.} & \textbf{Actual} \\
\midrule
\textsc{File\_Exists} & 5 & 1.00 & 0.99 & 1.00 \\
\textsc{Line\_Content} & 5 & 1.00 & 0.95 & 1.00 \\
\textsc{Function\_Exists} & 10 & 1.00 & 0.85 & 1.00 \\
\textsc{Import\_Exists} & 9 & 1.00 & 0.80 & 1.00 \\
\textsc{Package\_Version} & 8 & 0.75 & 0.90 & 0.75 \\
\textsc{Function\_Called} & 4 & 1.00 & 0.65 & 1.00 \\
\textsc{Has\_Callers} & 3 & 1.00 & 0.65 & 1.00 \\
\textsc{Absence} & 2 & 1.00 & 0.60 & 1.00 \\
\textsc{File\_Classification} & 2 & 1.00 & 0.80 & 1.00 \\
\textsc{Gen.\_Or\_Vendored} & 1 & 1.00 & 0.85 & 1.00 \\
\textsc{Entry\_Point} & 1 & 1.00 & 0.65 & 1.00 \\
\midrule
\textbf{Overall} & \textbf{50} & \textbf{0.96} & --- & --- \\
\bottomrule
\end{tabular}
\end{table}

The aggregate ECE is 0.167, indicating that confidence values are systematically conservative: actual accuracy exceeds predicted confidence for most types. This is a desirable property (the system underpromises), but the gap suggests confidence values could be raised after larger-scale validation. \textsc{Package\_Version} is the exception: its 0.90 confidence overestimates the 0.75 actual accuracy, driven by Go module path handling edge cases.
