\documentclass[sigconf,review,anonymous]{acmart}

\usepackage{booktabs}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{amsthm}

\newtheorem{definition}{Definition}

\acmConference[ICSE '27]{49th International Conference on Software Engineering}{April 2027}{Hyderabad, India}

\begin{document}

\title{CodeClaimVerifier: Deterministic Verification of LLM Claims About Source Code}

\author{Anonymous}
\affiliation{
  \institution{Anonymous Institution}
}

\begin{abstract}
Large language models increasingly reason about source code for security triage, code review, and refactoring. Their reasoning contains factual assertions -- ``function X has no callers,'' ``package version is 2.4.1,'' ``the file is auto-generated'' -- that drive downstream decisions. But LLMs hallucinate, and no systematic mechanism exists to verify these code-specific claims.

We present CodeClaimVerifier (CCV), a system that extracts typed claims from LLM reasoning and verifies each one deterministically against the actual codebase. CCV uses a single LLM call for claim extraction and zero LLM calls for verification, relying instead on grep, file reads, and lockfile parsing. Our 14-type claim taxonomy covers file existence, function definitions, call relationships, package versions, and absence assertions. A claim chaining mechanism infers dependencies between claims and propagates refutation through the dependency graph.

% [PLACEHOLDER: Add key quantitative results after evaluation]
% CCV achieves X\% verification accuracy on Y annotated claims across Z repositories,
% catching N\% of hallucinations that LLM-as-judge verification misses.

CCV is implemented as a standalone Python library with zero external dependencies, supporting custom claim types, batch verification with adaptive batching, and an evaluation framework. The system is domain-agnostic, applicable to any LLM output that makes assertions about source code.
\end{abstract}

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011066</concept_id>
<concept_desc>Software and its engineering~Software verification and validation</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10010147.10010178.10010179</concept_id>
<concept_desc>Computing methodologies~Natural language processing</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Software verification and validation}
\ccsdesc[300]{Computing methodologies~Natural language processing}

\keywords{LLM hallucination, code verification, claim extraction, security triage, deterministic verification}

\maketitle

\input{sections/introduction}
\input{sections/background}
\input{sections/problem}
\input{sections/design}
\input{sections/evaluation}
\input{sections/discussion}
\input{sections/related}
\input{sections/conclusion}

\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

\end{document}
